hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2025-06-25 inst/manuscript/paper.Rmd
Typo
Remove the Table call

**Figure 2.** Effective value model fit and application for European Grayling. Panel A shows developmental rates (days to hatch) at five differrent average rearing temperatures and the corresponding model fit (blue line). Panel B uses the effective value model derived from the blue line in panel A to predict the effective value of daily average temperatures ranging from 2 to 14 °C. The dashed line is a 0.01 increase in effective value for every 1 °C increase as a point of reference.

@@

**Box 4.** Predicted days to hatch for three warmwater species with custom parameterizations using a random thermal regime with an ascending thermograph with a mean temperature of 16 °C over 30 days.

@@

# Tables

```{r kabletable, echo=FALSE}
df <- data.frame(
  date = c(
    "2000-01-01",
    "...",
    "2000-07-01",
    "...",
    "2000-12-31"
  ),
  temperature = c(
    2.51,
    "...",
    16.32,
    "...",
    3.13
  )
)

knitr::kable(df,
  booktabs = TRUE
)
```

>>>>

**Figure 2.** Effective value model fit and application for European Grayling. Panel A shows developmental rates (days to hatch) at five different average rearing temperatures and the corresponding model fit (blue line). Panel B uses the effective value model derived from the blue line in panel A to predict the effective value of daily average temperatures ranging from 2 to 14 °C. The dashed line is a 0.01 increase in effective value for every 1 °C increase as a point of reference.

@@

**Box 4.** Predicted days to hatch for three warmwater species with custom parameterizations using a random thermal regime with an ascending thermograph with a mean temperature of 16 °C over 30 days. Note:

@@
